---
output:
  word_document: default
  html_document: default
---

```
```{r}
library(tidyverse)
library(randomForest)
library(randomForestExplainer)
library(tidymodels)
library(mice)
```

```{r}
ames_competition_csv = ames_competition_csv %>% mutate(ID = as_factor(ID)) %>%
  mutate(MS_Zoning = as_factor(MS_Zoning)) %>%
  mutate(Lot_Area = as_factor(Lot_Area)) %>%
  mutate(Lot_Shape = as_factor(Lot_Shape)) %>%
  mutate(Neighborhood = as_factor(Neighborhood)) %>%
  mutate(Bldg_Type = as_factor(Bldg_Type)) %>%
  mutate(House_Style = as_factor(House_Style)) %>%
  mutate(Overall_Qual = as_factor(Overall_Qual)) %>%
  mutate(Overall_Cond = as_factor(Overall_Cond)) %>%
  mutate(Year_Built = as_factor(Year_Built)) %>%
  mutate(Year_Remod_Add = as_factor(Year_Remod_Add)) %>%
  mutate(Sale_Condition = as_factor(Sale_Condition)) %>%
  mutate(Sale_Type = as_factor(Sale_Type))
```


```{r}
library(readxl)
ames_student <- read_excel("C:/Users/Breydan Gorham/Downloads/ames_student.xlsx")
library(readxl)
ames_competition_csv <- read_excel("C:/Users/Breydan Gorham/Downloads/ames_competition.xlsx")
competition = ames_competition
x = rep("yes", times= 428)
Predictions =data.frame(x)

set.seed(1234)
imp_age = mice(ames_competition_csv, m=5, method='pmm', printFlag=FALSE)

ames_competition_csv_complete = complete(imp_age)
summary(ames_competition_csv_complete)

ames_competition_recipe = recipe(ID ~ Sale_Type, ames_competition_csv_complete ) %>%
  step_dummy(all_nominal(), -all_outcomes())

rf_model = rand_forest() %>%
  set_engine("ranger") %>%
  set_mode("classification")

ames_competition_csv_wflow =
  workflow() %>%
  add_model(rf_model) %>%
  add_recipe(ames_competition_recipe)
```

```{r}
ggplot(ames_student1, aes(x= MS_Zoning, y= Neighborhood)) +
  geom_point()

ggplot(ames_student1, aes(x= Lot_Shape, y= Lot_Area)) +
  geom_point()

ggplot(ames_student1, aes(x= Overall_Cond, y= Year_Built)) +
  geom_point()

```

